---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# HW3correlation

<!-- badges: start -->
[![R-CMD-check](https://github.com/SherryLi1234/HW3Correlation/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SherryLi1234/HW3Correlation/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

## Overview

The goal of HW3correlation is to provide functions that help you calculate the most common correlation values between two variables.

 * `cor_check`check if there is NA, empty cells, non-numeric, or unpaired values in each variable, and make sure there are at least 3 observations in each variable.
 * `cor_pearson`Calculate the Pearson correlation between two variables.
 * `cor_check`Calculate the Spearman correlation between two variables.
 * `cor_check`Calculate the Kendall’s tau-b between two variables.
 
 If you are new to this package, you can learn more about these functions in `vignette("Tutorial_for_HW3correlation")`.

## Installation

You can install the development version of HW3correlation from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SherryLi1234/HW3Correlation")
```

## Example

This is a basic example which shows you how to solve a common problem:

### Note: Demonstrate the functions using R's default dataset: mtcars

```{r example}
library(HW3correlation)
## basic example code

cor_check(mtcars$mpg,mtcars$cyl)
#> [[1]]
#> [1] "Pass: no NA and blank cells."
#> [[2]]
#> [1] "Pass: no non-numeric values."
#> [[3]]
#> [1] "Pass: The X and Y variable match each other."
#> [[4]]
#> [1] "Pass: Enough observation"

cor_pearson(mtcars$mpg,mtcars$cyl)
#> [1] -0.852162

cor_spearman(mtcars$mpg,mtcars$cyl)
#> [1] -0.7794172

cor_kendallB(mtcars$mpg,mtcars$cyl)
#> [1] -0.7953134

```


