---
title: "Tutorial_for_HW3correlation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial_for_HW3correlation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
) 
```

```{r setup}
library(HW3correlation)
library(DescTools)
library(stats)
```

## To use the function `cor_check`:

`cor_check` check the following issues and return the results:

1. If there is black cell or NA in x and y variable.
2. If there is non-numeric value in x and y variable.
3. If the length of x and y variable match with each other. In other words,the numbers of observation in x and y variable are the same.
4. If there are enough (n>=3) values in x and y variable.
```{r}
## Non-valid variables
x<-c(1,2,3,"4",5,"")
y<-c(8,"2")
cor_check(x,y)

## Valid variables
x<-c(1,2,3,4,5)
y<-c(8,7,5,5,4)
cor_check(x,y)
```

## To use the function `cor_pearson`:

If the x and y variable pass the all the check in `cor_check`, the function `cor_pearson` will return the Pearson correlation value between these two variables. Otherwise, it will return the results of `cor_check`.
```{r}
## Non-valid variables
x<-c(1,2,3,"4",5,"")
y<-c(8,"2")
cor_pearson(x,y)

## Valid variables
a<-c(1,2,3,4,5)
b<-c(8,7,5,5,4)
cor_pearson(a,b)

## Compare with existing function: cor(x,y,method="pearson")
HW3cor_pearson<-cor_pearson(mtcars$mpg,mtcars$cyl)
stats_cor_pearson<-cor(mtcars$mpg,mtcars$cyl,method="pearson")

# Test the correctness
all.equal(HW3cor_pearson,stats_cor_pearson)

# Test the efficiency
bench::mark(HW3cor_pearson,stats_cor_pearson)
```

## To use the function `cor_spearman`:

If the x and y variable pass the all the check in `cor_check`, the function `cor_spearman` will return the  Spearman correlation value between these two variables. Otherwise, it will return the results of `cor_check`.
```{r}
## Non-valid variables
x<-c(1,2,3,"4",5,"")
y<-c(8,"2")
cor_spearman(x,y)

## Valid variables
a<-c(1,2,3,4,5)
b<-c(8,7,5,5,4)
cor_spearman(a,b)

## Compare with existing function: cor(x,y,method="spearman")
HW3cor_spearman<-cor_spearman(mtcars$mpg,mtcars$cyl)
stats_cor_spearman<-cor(mtcars$mpg,mtcars$cyl,method="spearman")

# Test the correctness
all.equal(HW3cor_spearman,stats_cor_spearman)

# Test the efficiency
bench::mark(HW3cor_spearman,stats_cor_spearman)
```


## To use the function `cor_kendallB`:

If the x and y variable pass the all the check in `cor_check`, the function `cor_kendallB` will return the Kendall’s tau-b value between these two variables. Otherwise, it will return the results of `cor_check`.
```{r}
## Non-valid variables
x<-c(1,2,3,"4",5,"")
y<-c(8,"2")
cor_kendallB(x,y)

## Valid variables
a<-c(1,2,3,4,5)
b<-c(8,7,5,5,4)
cor_kendallB(a,b)

## Compare with existing function: cor(x,y,method="kendall")
HW3cor_kendallB<-cor_kendallB(mtcars$mpg,mtcars$cyl)
stats_cor_kendall<-cor(mtcars$mpg,mtcars$cyl,method="kendall")

# Test the correctness
all.equal(HW3cor_kendallB,stats_cor_kendall)

# Test the efficiency
bench::mark(HW3cor_kendallB,stats_cor_kendall)
```
